Running simulations of MultipleContactNeutralMigrat.nlogo

### 2024-02-02 RunSims.Rmd
Updates to ms

>>>>

# Shannon-Diversity  
#
mdl1 %>%  
  ggplot(aes(x = habitat_patch_size, y = calc_shannon_diversity_mean, color = factor(birds_dispersal_distance))) + 
  geom_line(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = .5) +
  geom_point(aes(group = interaction(birds_dispersal_distance, birth_rate_birds)),  size = 1.2) +
  geom_ribbon(aes(ymin = calc_shannon_diversity_ql, ymax = calc_shannon_diversity_qh, group = interaction(birds_dispersal_distance, birth_rate_birds), fill = factor(birds_dispersal_distance)), alpha = 0.3,colour=NA, show.legend = FALSE) +
  scale_color_viridis_d() + scale_fill_viridis_d() +
  facet_wrap(~ birth_rate_birds, ncol = 4) + 
  labs(color = "Dispersal\n distance") +
  theme_bw() + xlab("Habitat Patch Size") + ylab("Shannon Diversity") +
  theme(
    legend.position = c(0.94,0.83)
    )
